\chapter{Conclusion}

    Using GIXRD to determine relative composition of samples led to the development of three analysis methods. 
    Two of the methods utilized integration, and their results are more closely aligned. 
    One method used peak intensity ratios, and provides results that noticeably differ. 
    All three methods provide reasonable agreement as to the depth that each incident angle probed. 
    
    Due to the time constraints of the project, future work will be needed to discriminate the methods further to determine their effectiveness. 
    The Surface Physics team has been manufacturing a magnetron deposition machine which will be used to create bilayers of metal. 
    As part of the equipment that will be used to produce these bilayers is a quartz oscillator that will change frequency as metal gets deposited onto it. 
    This data can then be compared to the analysis methods contained herein to determine their correlation. 
    Future work will also be needed to introduce nonuniform layers to the methods. 
    Preliminary work has been pursued, but much more time will be needed to get it fully integrated into the methods. 
    
    % Using GIXRD to reveal relative mixture amount dependent on depth has been shown to be useful in characterizing dopant samples, 
    % keeping in mind the limitations given by the assumptions.

% \section{Future Work}

%     Performing this analysis on a known sample would be able to provide greater validity to the results of this analysis.
%     Creating an analysis to correct for the real diffusion process by not assuming uniform layers.
%     This would produce the greatest impact on the real world application of these results.
    
    % Reformat the below to go into future work
    %The first of these assumptions is that the mixture of the probed depth is uniform, which is a known simplification of how the diffused dopants actually spread (an analysis to correct this has been tried, but better data is needed for it to be effective)